---
title: "Capstone"
author: "Jun Ming Li"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Libraries used

```{r}
library(ggplot2)
library(dplyr)
library(caret)
library(rpart)
library(randomForest)
library(readxl)
```


#Look at the data
```{r}
#Load the dataset
# flu <- read.csv("h1n1_fulldataset_CLEANED.csv") 
flu <- read.csv("h1n1_fulldataset_CLEANED_labels.csv") 
# This is all the datas from the competition put together, but we only need the labeled rows as our full dataset
# we are looking for the first 26707 rows

# confirmation
flu$h1n1_vaccine[[26707]]
flu$h1n1_vaccine[[26708]]

summary(flu)
str(flu)
head(flu)


# Check for NA values in the entire dataset
colSums(is.na(flu))

# Check if there are any NULLs (NULLs are rare in data frames but good to check)
any(sapply(flu,is.null))



```




#format data
```{r}

# format variables

## remove unnecessary variables
flu <- flu %>% dplyr::select(-c(respondent_id))
# These variables are removed for the following reasons:
# this is just an identification key

## Look at interesting variables
unique(flu$age_group)
#  "55 - 64 Years" "35 - 44 Years" "18 - 34 Years" "65+ Years"     "45 - 54 Years"
unique(flu$education)
# "< 12 Years"       "12 Years"         "College Graduate" "Some College"  

unique(flu$income_poverty)
# <= $75,000, Above Poverty > $75,000 Below Poverty

unique(flu$household_adults)
# 0 1 2 3

unique(flu$marital_status)
# married or not married

unique(flu$employment_status) # employed, unemployed, not in labor force

levels(flu$employment_industry) # 21 levels
levels(flu$employment_occupation) # 23 levels



levels(flu$employment_occupation) # 23 levels







## define categorical variables
flu <- flu %>% mutate(across(where(is.integer), as.factor))
flu <- flu %>% mutate(across(where(is.character), as.factor))


head(flu)
str(flu)
# possible issue with  industry and occupation variables. We may need to remove that. 




# This code will subset the portion of the data that will be our full data set, the first 26707 rows
flu_labels <- flu %>% filter(h1n1_vaccine == 1|h1n1_vaccine == 0)



# Flu is our whole data set, but does not include all the labels for everyone (no vaccination status provided for testing)
# flu_labels is our training data set with vaccination status




# Create new column for vaccination status
# 1 = no vaccination, 2 = h1n1vaccine, 3 = seasonal vaccine, 4 = both


flu_labels$Vaccination_General <- case_when(flu_labels$h1n1_vaccine == 0 & flu_labels$seasonal_vaccine == 0 ~ 0,
                                              flu_labels$h1n1_vaccine == 1 & flu_labels$seasonal_vaccine == 0 ~ 1,
                                              flu_labels$h1n1_vaccine == 0 & flu_labels$seasonal_vaccine == 1 ~ 2,
                                              flu_labels$h1n1_vaccine == 1 & flu_labels$seasonal_vaccine == 1 ~ 3)

flu_labels$Vaccination_General <- as.factor(flu_labels$Vaccination_General)



# 
# flu_labels$doctor_recc_General <- case_when(flu_labels$doctor_recc_h1n1 == 0 & flu_labels$doctor_recc_seasonal == 0 ~ 0,
#                                               flu_labels$doctor_recc_h1n1 == 1 & flu_labels$doctor_recc_seasonal == 0 ~ 1,
#                                               flu_labels$doctor_recc_h1n1 == 0 & flu_labels$doctor_recc_seasonal == 1 ~ 2,
#                                               flu_labels$doctor_recc_h1n1 == 1 & flu_labels$doctor_recc_seasonal == 1 ~ 3)
# 
# flu_labels$doctor_recc_General <- as.factor(flu_labels$Vaccination_General)





# remove
flu_labels$h1n1_vaccine <- NULL
flu_labels$seasonal_vaccine <- NULL
# flu_labels$doctor_recc_h1n1 <- NULL
# flu_labels$doctor_recc_seasonal <- NULL
```


# Save a copy of the data set to use.
```{r}

# write.csv(x = flu_labels, file = 'Final_h1n1_fulldataset_CLEANED_Labels.csv')

```





#EDA 
```{r}

## Subset the numerical and categorical variables for Flu
numeric_var <- flu %>% dplyr::select(where(is.numeric))
num_names   <- names(numeric_var)
cat_var     <- flu %>% dplyr::select(-num_names)



## Subset the numerical and categorical variables for flu_labels
numeric_var2 <- flu_labels %>% dplyr::select(where(is.numeric))
num_names2   <- names(numeric_var)
cat_var2     <- flu_labels %>% dplyr::select(-num_names)


# Flu is our whole data set, but does not include all the labels for everyone (no vaccination status provided for testing)
# flu_labels is our training data set with vaccination status


```





# EDA Charts for flu_labels
```{r}


# str(flu_labels)
# 
# # create bar charts for all cat var
#   for (var in names(cat_var2)) {
#     print(ggplot(cat_var2, aes(x = cat_var2[[var]], fill = Vaccination_General)) +
#     geom_bar() +
#     labs(title = paste("Histogram of", var), x = var))
# }

# 1 = no vaccination, 2 = h1n1vaccine, 3 = seasonal vaccine, 4 = both?



# h1n1 concern - highest level of concern has the lowest nonvac rates. 
# h1n1 knowledge - surprising to see large number of nonvax know about h1n1 at the time.
# avoidance behavior - high degree of nonvax in both categories
# houshold_children - seems to be the highest % of nonvax in no children households
# chronic medical condition - much higher % of nonvax for those without chronic conditions
# Opinions on vaccination effectiveness - the less they believe is it effective, the higher the non vax rate
# geo_region, race, education, age, occupation/employment - take a look at this through a % total, will need to do additional EDA for this


```





# Recombine the vaccination status to either no (0) or yes(1)?
```{r}
# Use ordered logit so that we can see the effects on each case


# flu_labels$Vaccination_General <- as.integer(flu_labels$Vaccination_General)
# 
# flu_labels$Vaccination_General <- case_when(flu_labels$h1n1_vaccine == 0 & flu_labels$seasonal_vaccine == 0 ~ 0,
#                                               flu_labels$h1n1_vaccine == 1 & flu_labels$seasonal_vaccine == 0 ~ 1,
#                                               flu_labels$h1n1_vaccine == 0 & flu_labels$seasonal_vaccine == 1 ~ 1,
#                                               flu_labels$h1n1_vaccine == 1 & flu_labels$seasonal_vaccine == 1 ~ 1)
# 
# flu_labels$Vaccination_General <- as.factor(flu_labels$Vaccination_General)
# 

```





#EDA after recombining the statuses
```{r}

# Subset the numerical and categorical variables for Flu
numeric_var <- flu %>% dplyr::select(where(is.numeric))
num_names   <- names(numeric_var)
cat_var     <- flu %>% dplyr::select(-num_names)



## Subset the numerical and categorical variables for flu_labels
numeric_var2 <- flu_labels %>% dplyr::select(where(is.numeric))
num_names2   <- names(numeric_var)
cat_var2     <- flu_labels %>% dplyr::select(-num_names)


# Flu is our whole data set, but does not include all the labels for everyone (no vaccination status provided for testing)
# flu_labels is our training data set with vaccination status


```







# EDA Charts after recombining the statuses
```{r}

# # create bar charts for all cat var
#   for (var in names(cat_var2)) {
#     print(ggplot(cat_var2, aes(x = cat_var2[[var]], fill = Vaccination_General)) +
#     geom_bar() +
#     labs(title = paste("Histogram of", var), x = var))
# }
```


# Correlation matrix

```{r}

# install.packages('DescTools')

# Load necessary libraries
library(dplyr)
library(DescTools)

# Get the names of the categorical variables
var_names <- names(cat_var2)
n <- length(var_names)

# Initialize an empty matrix to store corrected Cramer's V values
cramer_matrix <- matrix(NA, nrow = n, ncol = n)
rownames(cramer_matrix) <- var_names
colnames(cramer_matrix) <- var_names

# Loop through each pair of categorical variables to compute corrected Cramer's V
for (i in 1:n) {
  for (j in i:n) {
    if (i == j) {
      cramer_matrix[i, j] <- 1  # A variable is perfectly associated with itself
    } else {
      # Create a contingency table between variable i and variable j
      tbl <- table(cat_var2[[i]], cat_var2[[j]])
      # Compute corrected Cramer's V (with bias correction)
      cv <- CramerV(tbl, bias.correct = TRUE)
      cramer_matrix[i, j] <- cv
      cramer_matrix[j, i] <- cv  # Fill in the symmetric element
    }
  }
}

# Print the corrected Cramer's V matrix
print(cramer_matrix)



library(ggplot2)
library(reshape2)


# Convert the matrix into long format data frame using melt()
heatmap_df <- melt(cramer_matrix)

# Create the heat map with ggplot2
ggplot(heatmap_df, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "steelblue") +
  labs(title = "Cramer's V - All Variables", 
       x = NULL, 
       y = NULL, 
       fill = "Cramer's V") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), text = element_text(size=9))





```




## Partition data

```{r}

set.seed(123)

# Partition data into training (70%) and testing (30%) data sets

# create a sample of indexes
flu_labels.rows <- nrow(flu_labels)
flu_labels.index <- sample(flu_labels.rows, .7*flu_labels.rows)

# create datasets using above randomly chosen indexes
flu_labels.train <- flu_labels[flu_labels.index,]
flu_labels.test  <- flu_labels[-flu_labels.index,]

# confirm the total number of rows matches the above
nrow(flu_labels.test) + nrow(flu_labels.train)


```





## Balance the data

```{r}

# str(flu_labels.train)

table(flu_labels.train$Vaccination_General)
table(flu_labels.train$Vaccination_General)/nrow(flu_labels.train)

#   0    1    2    3 
# 9256  693 5441 3304 
# 
#          0          1          2          3 
# 0.49513213 0.03707072 0.29105595 0.17674120 


# 0 = No vaccination at all
# 1 = h1n1
# 2 = seasonal
# 3 = both vaccinated


# we have 4 classes


library(caret)

# oversampling
# Remove the outcome from the predictors.
predictors <- flu_labels.train[, setdiff(names(flu_labels.train), "Vaccination_General")]

# Use upSample to oversample the minority classes:
balancedData <- upSample(x = predictors,
                         y = flu_labels.train$Vaccination_General)

# The resulting data frame will have all predictors and an outcome column named "Class"
head(balancedData)
table(balancedData$Class)



# # undersampling
# # Separate the predictors and the outcome variable.
# predictors <- flu_labels.train[, setdiff(names(flu_labels.train), "Vaccination_General")]
# outcome <- flu_labels.train$Vaccination_General
# 
# # Use downSample() to create a balanced dataset by undersampling the majority classes.
# # The resulting data frame will include all predictors and an outcome column named "Class".
# balancedData <- downSample(x = predictors, y = outcome)
# 
# # Check the distribution of the outcome in the balanced data.
# table(balancedData$Class)




# Save the balanced dataset
flu_labels.train <- balancedData

#Restore original variable
flu_labels.train <- flu_labels.train %>% mutate(Vaccination_General = Class)
flu_labels.train$Class <- NULL
(table(flu_labels.train$Vaccination_General)) / nrow(flu_labels.train)


#   0    1    2    3 
# 9256  693 5441 3304 Before balance
# 9256 9256 9256 9256 After Balance
```




# create file for balanced training dataset

```{r}

# #install.packages("writexl")
# 
# library(writexl)
# 
# # Downloading the training dataset
# write.csv(x = flu_labels.train, file = 'balanced flu_labels.train.csv')


```








# Baseline accuracy
```{r}

table(flu_labels$Vaccination_General)

#vaccination over non vax accuracy
977 + 7738  + 4697 

13295/(13295+13412) 
# 50%
 
977 /(13295+13412) 
# 4%

7738 /(13295+13412) 
# 29%

4697 /(13295+13412) 
# 17%

```






# Multinominal Logistic Model with self selections

```{r}

# install.packages("nnet")

library(nnet)



#multinom# flu_labels.train$Vaccination_General

logit.reg.mlr.ss <- multinom(Vaccination_General ~.


-behavioral_avoidance
-behavioral_large_gatherings
-behavioral_touch_face
-child_under_6_months
-health_worker
-employment_status
-census_msa
-employment_occupation

, data =  flu_labels.train)
summary(logit.reg.mlr.ss)

# Look to see if there are potential outliers
# plot(logit.reg.ss)




```





# Calculate Pvalues MNL regression and remove more variables based on pvalue with threshold > .05:

```{r}


# Display the summary of the final model selected by stepwise regression
# summary(logit.reg.mlr.ss)

# Extract coefficients and standard errors from the summary
coefficients <- summary(logit.reg.mlr.ss)$coefficients
std_err <- summary(logit.reg.mlr.ss)$standard.errors

# Compute z-statistics: coefficient / standard error
z_values <- coefficients / std_err

# Calculate the two-tailed p-values based on the normal distribution:
p_values <- 2 * (1 - pnorm(abs(z_values)))
# print(p_values)



# Define significance threshold
alpha <- 0.05

# Exclude the intercept column(s)
p_vals_no_int <- p_values[, !grepl("(Intercept)", colnames(p_values)), drop = FALSE]

# Define the predictor names (the prefixes in your coefficient names)

namesall<-names(flu_labels.train)

drop_names <- c("behavioral_avoidance", "behavioral_large_gatherings", "behavioral_touch_face",
                "child_under_6_months", "health_worker", "employment_status",
                "census_msa", "employment_occupation", "Vaccination_General")

namesall <- namesall[!namesall %in% drop_names]


predictor_names <- c(namesall)

# Initialize vector to store names of predictors considered insignificant
insignificant_predictors <- c()


# Loop through each predictor and check its coefficients' p-values
for (pred in predictor_names) {
  # Get all columns whose names begin with the predictor name.
  pred_cols <- grep(pred, colnames(p_vals_no_int), value = TRUE)
  # Extract the corresponding p-values (this will be a submatrix; even if it's just one column)
  p_vals_pred <- p_vals_no_int[, pred_cols, drop = FALSE]

  # Check if all p-values for this predictor across all outcomes are > alpha.
  if (all(p_vals_pred > alpha)) {
    insignificant_predictors <- c(insignificant_predictors, pred)
  }
}

# Print predictors that are not significant across the outcomes
print("Predictors deemed insignificant (all levels p > alpha):")
print(insignificant_predictors)



```





# Accuracy with self select multinominal model

```{r}

# Predicted.test.prob is a data frame with predicted probabilities for each class,
# with columns named "0", "1", "2", and "3".
predicted.test.prob <- predict(logit.reg.mlr.ss, newdata = flu_labels.test, type = "probs")
predicted.test.prob <- data.frame(predicted.test.prob)
head(predicted.test.prob)

# Instead of using a 0.5 cutoff on each column (which returns 4 columns),
# we select the class with the highest probability for each observation.
# max.col() returns the column index of the maximum probability for each row.
predicted_class <- colnames(predicted.test.prob)[max.col(predicted.test.prob, ties.method = "first")]

# Convert to the class naming convention of Vaccination_General
predicted_class <- ifelse(predicted_class == "X0",0,
                   ifelse(predicted_class == "X1",1,
                   ifelse(predicted_class == "X2",2,
                   ifelse(predicted_class == "X3",3,"NA"))))



# Convert the resulting character vector into a factor with the same levels as your reference variable.
predicted_class <- factor(predicted_class, levels = levels(flu_labels.test$Vaccination_General))

# Load the caret package and create the confusion matrix.
library(caret)
confusionMatrix(data = predicted_class, reference = flu_labels.test$Vaccination_General)



# Checking the AUC for a multinomial logistic regression
library(pROC)

# Calculate multiclass ROC.
# The 'predicted.test.prob' should be a matrix (or data frame) of class probabilities,
# with one column per class.
predicted.test.prob <- predict(logit.reg.mlr.ss, newdata = flu_labels.test, type = "probs")
roc_multi <- multiclass.roc(flu_labels.test$Vaccination_Genera, predicted.test.prob)

# Print the overall AUC (this is an average of the pairwise AUCs)
auc_multi <- auc(roc_multi)
print(paste("Multiclass AUC:", auc_multi))

# Plot one of the pairwise ROC curves (for example, the first one).
# Note: Each element in 'roc_multi$rocs' corresponds to a one-vs-one ROC.

table(flu_labels.test$Vaccination_General)

# roc_multi$rocs[[1]][[2]]
# roc_multi$rocs[[2]][[2]]
# roc_multi$rocs[[3]][[2]]


plot(roc_multi$rocs[[1]][[2]], col='red' ,main="ROC Curve (Pairwise) for Multinomial Logistic Regression")
plot(roc_multi$rocs[[2]][[2]],col = 'blue', add=TRUE)
plot(roc_multi$rocs[[3]][[2]],col = 'green', add=TRUE)

# Add a legend to differentiate between the curves
legend("bottomright",
       legend = c("H1n1 Vaccination", 
                  "Seasonal Vaccination", 
                  "Both Vaccination"),
       col = c("red", "blue", "green"),
       lwd = 2)



```






```{r}
names(flu_labels)
```





# Multinomial backward stepwise selection model

```{r}

library(MASS)

# Fit a full multinomial logistic regression model using all predictors
full_model <- multinom(Vaccination_General ~.

-behavioral_avoidance
-behavioral_large_gatherings
-behavioral_touch_face
-child_under_6_months
-health_worker
-employment_status
-census_msa
-employment_occupation
#additional from the pvalue analysis from above
-behavioral_outside_home
# -rent_or_own
# -household_adults
, data =  flu_labels.train)


# Perform stepwise model selection based on AIC
# direction = "both" allows both forward selection and backward elimination.
step_model_backward <- stepAIC(full_model, direction = "backward", trace = FALSE)

# Display the summary of the final model selected by stepwise regression
summary(step_model_backward)


```



As a general rule of thumb, lower AIC is better, but there are degrees to it. 

Differences in AIC Values:

Difference < 2: The models are nearly indistinguishable; both could be considered good.

Difference 4–7: There is moderate evidence against the model with the higher AIC.

Difference > 10: There is strong evidence that the model with the lower AIC is much better.

What Makes for a Good or Bad AIC?



AIC from our own selection:

Residual Deviance: 30317.72 
AIC: 30845.72 
Residual Deviance: 74895.8 
AIC: 75423.8 



AIC from our backward selection selection:

Residual Deviance: 30341.98  
AIC: 30839.98 

Residual Deviance: 74895.77 
AIC: 75411.77 



# Calculate Pvalues of backward regression and remove more variables based on pvalue with threshold > .01:

```{r}

# Display the summary of the final model selected by stepwise regression
# summary(step_model_backward)

# Extract coefficients and standard errors from the summary
coefficients <- summary(step_model_backward)$coefficients
std_err <- summary(step_model_backward)$standard.errors

# Compute z-statistics: coefficient / standard error
z_values <- coefficients / std_err

# Calculate the two-tailed p-values based on the normal distribution:
p_values <- 2 * (1 - pnorm(abs(z_values)))
# print(p_values)



# Define significance threshold
alpha <- 0.01

# Exclude the intercept column(s)
p_vals_no_int <- p_values[, !grepl("(Intercept)", colnames(p_values)), drop = FALSE]

# Define the predictor names (the prefixes in your coefficient names)

namesall<-names(flu_labels.train)

drop_names <- c("behavioral_avoidance", "behavioral_large_gatherings", "behavioral_touch_face",
                "child_under_6_months", "health_worker", "employment_status",
                "census_msa", "employment_occupation", "Vaccination_General",
                "behavioral_outside_home")


namesall <- namesall[!namesall %in% drop_names]


predictor_names <- c(namesall)

# Initialize vector to store names of predictors considered insignificant
insignificant_predictors <- c()


# Loop through each predictor and check its coefficients' p-values
for (pred in predictor_names) {
  # Get all columns whose names begin with the predictor name.
  pred_cols <- grep(pred, colnames(p_vals_no_int), value = TRUE)
  # Extract the corresponding p-values (this will be a submatrix; even if it's just one column)
  p_vals_pred <- p_vals_no_int[, pred_cols, drop = FALSE]

  # Check if all p-values for this predictor across all outcomes are > alpha.
  if (all(p_vals_pred > alpha)) {
    insignificant_predictors <- c(insignificant_predictors, pred)
  }
}

# Print predictors that are not significant across the outcomes
print("Predictors deemed insignificant (all levels p > alpha):")
print(insignificant_predictors)

# No values for alpha = .05
# If we get no insignificant predictors here, we can lower the threshold level to .01 for absolute refinement.

```

For the initial self selection model, 8 variables removed from group discussion
-behavioral_avoidance
-behavioral_large_gatherings
-behavioral_touch_face
-child_under_6_months
-health_worker
-employment_status
-census_msa
-employment_occupation


After the initial self selection mode, 1 more removed through analysis of pvalues
-behavioral_outside_home



Backwards was done with updated list, removing the above 9 in total, using stricter threshold of .01, 1 more variables removed. 
-martial_status



Per Mazen's idea, combined the doc_recc variables togethers, but have a new category. replicate the same logic as vaccination general 
did not work, skewed results too much








# Accuracy of backward multinominal model

```{r}

# Predicted.test.prob is a data frame with predicted probabilities for each class,
# with columns named "0", "1", "2", and "3".
predicted.test.prob <- predict(step_model_backward, newdata = flu_labels.test, type = "probs")
predicted.test.prob <- data.frame(predicted.test.prob)
head(predicted.test.prob)

# Instead of using a 0.5 cutoff on each column (which returns 4 columns),
# we select the class with the highest probability for each observation.
# max.col() returns the column index of the maximum probability for each row.
predicted_class <- colnames(predicted.test.prob)[max.col(predicted.test.prob, ties.method = "first")]

# Convert to the class naming convention of Vaccination_General
predicted_class <- ifelse(predicted_class == "X0",0,
                   ifelse(predicted_class == "X1",1,
                   ifelse(predicted_class == "X2",2,
                   ifelse(predicted_class == "X3",3,"NA"))))



# Convert the resulting character vector into a factor with the same levels as your reference variable.
predicted_class <- factor(predicted_class, levels = levels(flu_labels.test$Vaccination_General))

# Load the caret package and create the confusion matrix.
library(caret)
confusionMatrix(data = predicted_class, reference = flu_labels.test$Vaccination_General)



# Checking the AUC for a multinomial logistic regression
library(pROC)

# Calculate multiclass ROC.
# The 'predicted.test.prob' should be a matrix (or data frame) of class probabilities,
# with one column per class.
predicted.test.prob <- predict(step_model_backward, newdata = flu_labels.test, type = "probs")
roc_multi <- multiclass.roc(flu_labels.test$Vaccination_Genera, predicted.test.prob)

# Print the overall AUC (this is an average of the pairwise AUCs)
auc_multi <- auc(roc_multi)
print(paste("Multiclass AUC:", auc_multi))

# Plot one of the pairwise ROC curves (for example, the first one).
# Note: Each element in 'roc_multi$rocs' corresponds to a one-vs-one ROC.

table(flu_labels.test$Vaccination_General)

# roc_multi$rocs[[1]][[2]]
# roc_multi$rocs[[2]][[2]]
# roc_multi$rocs[[3]][[2]]


plot(roc_multi$rocs[[1]][[2]], col='red' ,main="ROC Curve (Pairwise) for Multinomial Logistic Regression")
plot(roc_multi$rocs[[2]][[2]],col = 'blue', add=TRUE)
plot(roc_multi$rocs[[3]][[2]],col = 'green', add=TRUE)

# Add a legend to differentiate between the curves
legend("bottomright",
       legend = c("H1n1 Vaccination", 
                  "Seasonal Vaccination", 
                  "Both Vaccination"),
       col = c("red", "blue", "green"),
       lwd = 2)



```




















# FINAL VARIABLE SELECTION

```{r}

# install.packages("nnet")

library(nnet)



#multinom# flu_labels.train$Vaccination_General

logit.reg.mlr.ff <- multinom(Vaccination_General ~. 

-doctor_recc_h1n1
-doctor_recc_seasonal
-health_insurance
-opinion_h1n1_risk
-opinion_seas_vacc_effective
-opinion_seas_risk
-age_group
-employment_industry
-h1n1_concern
-h1n1_knowledge
-chronic_med_condition
-race
-sex
-income_poverty
, data =  flu_labels.train)
summary(logit.reg.mlr.ff)

# Look to see if there are potential outliers
# plot(logit.reg.ff)



```










# Calculate Pvalues of FINAL VAR SELECTION

```{r}


# Display the summary of the final model selected by stepwise regression
# summary(logit.reg.mlr.ff)

# Extract coefficients and standard errors from the summary
coefficients <- summary(logit.reg.mlr.ff)$coefficients
std_err <- summary(logit.reg.mlr.ff)$standard.errors

# Compute z-statistics: coefficient / standard error
z_values <- coefficients / std_err

# Calculate the two-tailed p-values based on the normal distribution:
p_values <- 2 * (1 - pnorm(abs(z_values)))
# print(p_values)



# Define significance threshold
alpha <- 0.05

# Exclude the intercept column(s)
p_vals_no_int <- p_values[, !grepl("(Intercept)", colnames(p_values)), drop = FALSE]

# Define the predictor names (the prefixes in your coefficient names)

namesall<-names(flu_labels.train)

drop_names <- c("behavioral_avoidance", "behavioral_large_gatherings", "behavioral_touch_face",
                "child_under_6_months", "health_worker", "employment_status",
                "census_msa", "employment_occupation", "Vaccination_General")

namesall <- namesall[!namesall %in% drop_names]


predictor_names <- c(namesall)

# Initialize vector to store names of predictors considered insignificant
insignificant_predictors <- c()


# Loop through each predictor and check its coefficients' p-values
for (pred in predictor_names) {
  # Get all columns whose names begin with the predictor name.
  pred_cols <- grep(pred, colnames(p_vals_no_int), value = TRUE)
  # Extract the corresponding p-values (this will be a submatrix; even if it's just one column)
  p_vals_pred <- p_vals_no_int[, pred_cols, drop = FALSE]
  
  # Check if all p-values for this predictor across all outcomes are > alpha.
  if (all(p_vals_pred > alpha)) {
    insignificant_predictors <- c(insignificant_predictors, pred)
  }
}

# Print predictors that are not significant across the outcomes
print("Predictors deemed insignificant (all levels p > alpha):")
print(insignificant_predictors)



```






# Accuracy with FINAL VAR SELECTION MODEL

```{r}

# Predicted.test.prob is a data frame with predicted probabilities for each class,
# with columns named "0", "1", "2", and "3".
predicted.test.prob <- predict(logit.reg.mlr.ff, newdata = flu_labels.test, type = "probs")
predicted.test.prob <- data.frame(predicted.test.prob)
head(predicted.test.prob)

# Instead of using a 0.5 cutoff on each column (which returns 4 columns), 
# we select the class with the highest probability for each observation.
# max.col() returns the column index of the maximum probability for each row.
predicted_class <- colnames(predicted.test.prob)[max.col(predicted.test.prob, ties.method = "first")]

# Convert to the class naming convention of Vaccination_General
predicted_class <- ifelse(predicted_class == "X0",0, 
                   ifelse(predicted_class == "X1",1,
                   ifelse(predicted_class == "X2",2,
                   ifelse(predicted_class == "X3",3,"NA"))))



# Convert the resulting character vector into a factor with the same levels as your reference variable.
predicted_class <- factor(predicted_class, levels = levels(flu_labels.test$Vaccination_General))

# Load the caret package and create the confusion matrix.
library(caret)
confusionMatrix(data = predicted_class, reference = flu_labels.test$Vaccination_General)



# Checking the AUC for a multinomial logistic regression
library(pROC)

# Calculate multiclass ROC.
# The 'predicted.test.prob' should be a matrix (or data frame) of class probabilities,
# with one column per class.
predicted.test.prob <- predict(logit.reg.mlr.ff, newdata = flu_labels.test, type = "probs")
roc_multi <- multiclass.roc(flu_labels.test$Vaccination_Genera, predicted.test.prob)

# Print the overall AUC (this is an average of the pairwise AUCs)
auc_multi <- auc(roc_multi)
print(paste("Multiclass AUC:", auc_multi))


# table(flu_labels.test$Vaccination_General)

#Each element in 'roc_multi$rocs' corresponds to a one-vs-one ROC.
# roc_multi$rocs[[1]][[2]]
# roc_multi$rocs[[2]][[2]]
# roc_multi$rocs[[3]][[2]]


plot(roc_multi$rocs[[1]][[2]], col='grey' ,main="ROC Curve (Pairwise) for Multinomial Logistic Regression")
plot(roc_multi$rocs[[2]][[2]],col = 'orange', add=TRUE)
plot(roc_multi$rocs[[3]][[2]],col = '#0073e6', add=TRUE)

# Add a legend to differentiate between the curves
legend("bottomright", 
       legend = c("H1n1 Vaccination", 
                  "Seasonal Vaccination", 
                  "Both Vaccination"), 
       col = c("grey", "orange", "#0073e6"), 
       lwd = 2)



```





# Code to export final probabilities from multiclass logistic regression

```{r}

#install.packages("writexl")
# library(writexl)
# 
# 
# flu_labels.test2 <- flu_labels.test
# 
# 
# flu_labels.test2$prediction01 <- predicted.test.prob$X0
# flu_labels.test2$prediction02 <- predicted.test.prob$X1
# flu_labels.test2$prediction03 <- predicted.test.prob$X2
# flu_labels.test2$prediction04 <- predicted.test.prob$X3
# 
# 
# 
# write.csv(x = flu_labels.test2, file = 'Final Logistic Predictions.csv')
# 


```






```{r}

flu_labels

library(ggplot2)

ggplot(flu_labels, aes(y=flu_labels$opinion_seas_vacc_effective, x=age_group)) +
  geom_boxplot()

table(flu_labels$opinion_seas_vacc_effective)

```







